\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-11-27 AffineLieAlgebras/InformalNotes/article.tex
LiterateLie in Scheme started, acms paper pdf added, some work on new article.

So we've obtained recurrent relation for the anomalous branching coefficients.  In the next section we describe the algorithm for the computation of branching coefficients using the relation \eqref{recurrent relation}.

@@

Consider the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the thick vectors at the figure \ref{fig:B2_A1}. We denote the corresponding Weyl reflections by $\omega_1, \omega_2$. Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+\alpha_2$.

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$. 
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (0,1),\; (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.
\begin{comment}
  It seems that here $\Gamma$ should include only two points. Is it true?

  Think of the pictures more.
\end{comment}
Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
\begin{equation}
  \label{eq:23}
  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0}_1 - 3\cdot \delta_{0,0} = 1
\end{equation}
So we've computed the branching coefficients.
\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
We calculate the branching coefficients for the fundamental representation of $B_4$.
The corresponding Dynkin diagrams are in the figure.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams}
  \label{fig:dynkin}
\end{figure}

@@

The set of the anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W$
consists of 384 points. We don't show it here.

@@

We show the result of this procedure on the figure \ref{fig:B4B2anom}.
\begin{figure}[h]
    \includegraphics[width=170mm]{B4_B2_anom_points.pdf}
  \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

@@

The set of the anomalous points of this representation up to sixth grade is depicted in the figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the figure \ref{fig:B2_A1}.

@@

As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented at the figure
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

Now we proceed the computation of the branching coefficients using the algorithm \ref{sec:algorithm}. 
On the level 1 there exist three dominant weights with Dynkin labels $[1,0,0], \; [0,1,0],\; [0,0,1]$.
\begin{comment}
  Do the calculation, show the restriction on the grade and the final result
  \begin{equation}
    \label{eq:35}
    Z=\left|\chi_{[10,0]}+\chi_{[4,6]}\right|^2+\left|\chi_{[7,3]}+\chi_{[3,7]}\right|^2+\left|\chi_{[6,4]}+\chi_{[0,10]}\right|^2
  \end{equation}
\end{comment}

>>>>

So we have obtained recurrent relation for the anomalous branching coefficients.  In the next section we describe the algorithm for the computation of branching coefficients using the relation \eqref{recurrent relation}.

@@

Consider the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the thick vectors at the Figure \ref{fig:B2_A1}. We denote the corresponding Weyl reflections by $\omega_1, \omega_2$. Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+\alpha_2$.

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the Figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$. 
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (0,1),\; (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.
\begin{comment}
  It seems that here $\Gamma$ should include only two points. Is it true?

  Think of the pictures more.
\end{comment}
Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
\begin{equation}
  \label{eq:23}
  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0}_1 - 3\cdot \delta_{0,0} = 1
\end{equation}
So we have computed the branching coefficients.
\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
We calculate the branching coefficients for the fundamental representation of $B_4$.
The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams}
  \label{fig:dynkin}
\end{figure}

@@

The set of the anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W$
consists of 384 points. We do not show it here.

@@

We show the result of this procedure on the Figure \ref{fig:B4B2anom}.
\begin{figure}[h]
    \includegraphics[width=170mm]{B4_B2_anom_points.pdf}
  \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

@@

The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.

@@

As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented at the Figure
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

Now we proceed the computation of the branching coefficients using the algorithm \ref{sec:algorithm}. 
On the level 1 there exist three dominant weights with Dynkin labels $[1,0,0], \; [0,1,0],\; [0,0,1]$.

\begin{comment}
  Do the calculation, show the restriction on the grade and the final result
  \begin{equation}
    \label{eq:35}
    Z=\left|\chi_{[10,0]}+\chi_{[4,6]}\right|^2+\left|\chi_{[7,3]}+\chi_{[3,7]}\right|^2+\left|\chi_{[6,4]}+\chi_{[0,10]}\right|^2
  \end{equation}
\end{comment}
